---
title: "hate speech detection"
author: "yassmine yazidi"
date: "2025-04-14"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Packages

```{r}
install.packages("quanteda")
install.packages("tm")
install.packages("SnowballC")
install.packages("wordcloud")
install.packages("e1071")
install.packages("gmodels")
install.packages("caret")
```

# Load and Explore Dataset

```{r}
comments_raw <- read.csv("HateSpeechDataset_4000.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
comments_raw$Label <- factor(comments_raw$Label)
str(comments_raw)
table(comments_raw$Label)
```

# Preprocess Text Data

```{r}
library(tm)
comment_corpus <- VCorpus(VectorSource(comments_raw$Content))
comments_corpus_cleaned <- tm_map(comment_corpus, content_transformer(tolower))
comments_corpus_cleaned <- tm_map(comments_corpus_cleaned, removeNumbers)
comments_corpus_cleaned <- tm_map(comments_corpus_cleaned, removeWords, stopwords())
comments_corpus_cleaned <- tm_map(comments_corpus_cleaned, removePunctuation)
library(SnowballC)
comments_corpus_cleaned <- tm_map(comments_corpus_cleaned, stemDocument)
comments_corpus_cleaned <- tm_map(comments_corpus_cleaned, stripWhitespace)
```

# Create Document-Term Matrix

```{r}
comment_dtm <- DocumentTermMatrix(comments_corpus_cleaned)
comment_dtm_train <- comment_dtm[1:2800, ]
comment_dtm_test <- comment_dtm[2801:4000, ]
comment_train_labels <- comments_raw[1:2800, ]$Label
comment_test_labels <- comments_raw[2801:4000, ]$Label
```

# Label Distribution in Train/Test Sets

```{r}
prop.table(table(comment_train_labels))
prop.table(table(comment_test_labels))
```

# Word Cloud: All Comments

```{r}
library(wordcloud)
wordcloud(comments_raw$Content, max.words = 50, random.order = FALSE)
```

# Word Cloud: Hate Comments

```{r}
hate_comments <- comments_raw$Content[comments_raw$Label == 1]
Hcorpus <- Corpus(VectorSource(hate_comments))
Hcorpus <- tm_map(Hcorpus, content_transformer(tolower))
Hcorpus <- tm_map(Hcorpus, removePunctuation)
Hcorpus <- tm_map(Hcorpus, removeWords, stopwords())
Hcorpus <- tm_map(Hcorpus, stripWhitespace)
wordcloud(Hcorpus, max.words = 30, colors = brewer.pal(8, "Reds"))
```

# Word Cloud: Not Hate Comments

```{r}
nhate_comments <- comments_raw$Content[comments_raw$Label == 0]
nHcorpus <- Corpus(VectorSource(nhate_comments))
nHcorpus <- tm_map(nHcorpus, content_transformer(tolower))
nHcorpus <- tm_map(nHcorpus, removePunctuation)
nHcorpus <- tm_map(nHcorpus, removeWords, stopwords())
nHcorpus <- tm_map(nHcorpus, stripWhitespace)
wordcloud(nHcorpus, max.words = 30, colors = brewer.pal(8, "Blues"))
```

# Prepare for Naive Bayes

```{r}
library(quanteda)
comment_freq_words <- findFreqTerms(comment_dtm_train, 5)
comments_dtm_freq_train <- comment_dtm_train[, comment_freq_words]
comments_dtm_freq_test <- comment_dtm_test[, comment_freq_words]
convert_counts <- function(x) {
  x <- ifelse(x > 0, "Yes", "No")
}
comments_train <- apply(comments_dtm_freq_train, MARGIN = 2, convert_counts)
comments_test <- apply(comments_dtm_freq_test, MARGIN = 2, convert_counts)
```

# Train the Naive Bayes Model

```{r}
library(e1071)
comments_classifer <- naiveBayes(comments_train, comment_train_labels)
```

# Evaluate Model

```{r}
library(gmodels)
comments_test_pred <- predict(comments_classifer, comments_test, laplace = TRUE)
CrossTable(comments_test_pred, comment_test_labels, prop.chisq = FALSE, prop.t = FALSE, dnn = c('Predicted', 'Actual'))
library(caret)
confusionMatrix(comments_test_pred, comment_test_labels)
```

# Prediction Function

```{r}
predict_hate <- function(input_text, model, dtm_template) {
  input_corpus <- Corpus(VectorSource(input_text))
  input_corpus <- tm_map(input_corpus, content_transformer(tolower))
  input_corpus <- tm_map(input_corpus, removePunctuation)
  input_corpus <- tm_map(input_corpus, removeNumbers)
  input_corpus <- tm_map(input_corpus, removeWords, stopwords("english"))
  input_corpus <- tm_map(input_corpus, stripWhitespace)
  input_dtm <- DocumentTermMatrix(input_corpus, control = list(dictionary = Terms(dtm_template)))
  input_matrix <- as.data.frame(as.matrix(input_dtm))
  prediction <- predict(model, input_matrix)
  return(ifelse(prediction == 1, "Hate Speech", "Not Hate"))
}

# Example Test

```{r}
text <- "try to look for a different picture to share on insta you ugly slut hhhhhh"
predict_hate(text, comments_classifer, comment_dtm)
